---
title: "Introduction to HW2 Three Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to HW2 Three Functions}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW2 Function

The R package `HW2` contains three functions: `solve_ols()`, `algo_leverage()` and `elnet_coord()`. In those functions, the following packages `Matrix`, `stats` and `MASS` are used. These three functions deal with the corresponding three problems in the HW1 and we will demonstrate the usage of them in this article. 

`HW2` can be loaded using the `library` command:
```{r, message=FALSE}
library(HW2)
```
### solve_ols() Function

For `solve_ols(X,b,method,tol=1e-4)` function, this function solves a linear system using Gauss-Seidel or Jacobi method. It takes four arguments as following. 

$X$: the coefficient matrix of the linear system and should be a square matrix.

$b$: the column vector collects values of each linear equation. 

$method$: the method is used to solve the linear system, either "Gauss" or "Jacobi" coresponding to Gauss-Seidel or Jacobi method respectively.

$tol$: the convergence criterion which is measured by the l_2 norm of the difference of between the current solution and the solution in the last iteration. The default value is $10^{-4}$.

`solve_ols()` will return the solution vector of the linear system specified in the function.

One usage example is as follows:
```
# Generate X and b as in HW1
alpha=2
L=odiag(c(rep(-1,99)),-1)
U=odiag(c(rep(-1,99)),1)
D=diag(alpha,100,100)
X=L+U+D
v=matrix(c(rep(c(1,0),50)),ncol=1)
b=X%*%v

# Gauss-Seidel method
v_gauss=solve_ols(X=X,b=b,method="Gauss")

# Jacobi method
v_jocobi=solve_ols(X=X,b=b,method="Jacobi")
```

### algo_leverage() Function

For `algo_leverage` function, this function implements algorithmic leveraging for linear regression using uniform and leverage score based subsampling of rows. More specifically, the simulation setting of Figure 1 in https://onlinelibrary.wiley.com/doi/full/10.1002/wics.1324 is considered.

The function will automatically generate the simulation setting in previous paper, so it does not take any arguments.

`algo_leverage()` will return a list contains two numeric vectors, the simulated design matrix $X$, the simulated response matrix $Y$. The two numeric vectors corresponding to uniform sampling (beta_unif) and leverage sampling (beta_lev). Each vector contains regression coefficients obtained using r = 10, 50, 100, 200, 300 in order.

One usage example is as follows:
```
result=algo_leverage()
# simulated design matrix
X=result$X
# simulated response matrix
Y=result$Y
# uniform sampling regression coefficients 
beta_unif=result$beta_unif
# leverage sampling regression coefficients
beta_lev=result$beta_lev
```


### elnet_coord() Function

For `elnet_coord()` function, this function fits elastic net to data using coordinate descent algorithm. 

The function will automatically generate the simulation setting is specified in homework 1 problem 3 part 2, so it does not take any arguments.

The function will return a numeric vector of regression coefficients, the simulated design matrix $X$, the simulated response matrix $Y$ and together with a solution path plot shown in the plots panel.

One usage example is as follows:
```
result=elnet_coord()
# simulated design matrix
X=result$X
# simulated response matrix
Y=result$Y
# regression coefficients 
beta=result$beta_co
```

